---
title: "Pilot Analysis Full - Comprehension and Attention Checks "
output:
  pdf_document: default
  html_notebook: default
---

This document summarises outcomes of the comprehension and attention checks for the full pilot pairs analysis. Please see the script for further details. 

```{r setup, include = FALSE}
library('groundhog')
groundhog.library(
  c(
    'papaja', #for apa formatting
    'pwr', # for power calculation
    'tidyverse', # for pipe %>%
    'emmeans',
    'afex',
    'dplyr'
  ), "2024-04-15"
)
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, results='hide')
```


```{r}
#Creating the filtered dataframe 
pilot.df <- read.csv("combined_pilot_batches.csv", na=c("")) %>%
  filter(!(word %in% c('', 'ZEBRA'))) %>%
  mutate(subj_id=PROLIFIC_PID)
pilot.df

data_from_games <- pilot.df %>%
  filter(trial_type=='Hangman_replay') %>%
  dplyr::select(subj_id,word,num_clicks) 
data_from_games

data_from_confidence <- read.csv("combined_pilot_batches.csv") %>%
  mutate(subj_id=PROLIFIC_PID,
         confidence=as.numeric(confidence_slider_self_response)) %>%
  group_by(subj_id) %>%
  summarise(
    confidence=mean(confidence,na.rm=T)
  )
data_from_confidence

data_from_guesses <- pilot.df %>%
  filter(trial_type=='Guess_leaderboard') %>%
  dplyr::select(subj_id,subject_pair,word,position,position_RT,true_position,reveal_word,player,distance, self_rating)
data_from_guesses
          
#Merge above to new usable, filtered dataframe
filtered_df <- data_from_games %>%
  merge(data_from_guesses) %>%
  merge(data_from_confidence)
filtered_df

#Change variables from characters to correct classification 
#Change reveal_word into a categorical variable
filtered_df$reveal_word <- factor(filtered_df$reveal_word)
#Change position into an integer variable 
filtered_df$position <- as.integer(filtered_df$position)
#Change true_position into an integer variable
filtered_df$true_position <- as.integer(filtered_df$true_position)
#Change distance into an integer variable 
filtered_df$distance <- as.integer(filtered_df$distance)
#Change self-rating into an integer
filtered_df$self_rating <- as.integer(filtered_df$self_rating)
#Change word into a categorical variable 
filtered_df$word <- factor(filtered_df$word)

#Check variables were changed correctly
#Check class reveal_word
class(filtered_df$reveal_word)
#Check class position 
class(filtered_df$position)
#Check class true position 
class(filtered_df$true_position)
#check class distance 
class(filtered_df$distance)
#check class self rating
class(filtered_df$self_rating)
#check class word 
class(filtered_df$word)

#Rename levels of reveal_word from true and false to revealed and hidden, respectively 
filtered_df$reveal_word <- factor(filtered_df$reveal_word, levels = c("true", "false"), labels = c("revealed", "hidden"))

# Check the levels of reveal_word variable
levels(filtered_df$reveal_word)

#Check changes in filtered_df (whcih we will be using for our analysis)
print(filtered_df)
```


```{r}
#Create relevant dataframes
data_from_comprehension <- pilot.df %>%
  filter(trial_type== 'survey-multi-choice') %>%
  dplyr::select(subj_id, correct, test_part)
data_from_comprehension

data_from_attention <- pilot.df %>%
  filter(trial_type== 'survey-text') %>%
  dplyr::select(subj_id, last_word)
data_from_attention
```

# Comprehension Checks

```{r}
#Focusing on data from comprehension 
# Convert 'correct' to logical if needed
data_from_comprehension$correct <- as.logical(data_from_comprehension$correct)
#change test_part into a categorical variable 
data_from_comprehension$test_part <- factor(data_from_comprehension$test_part)
data_from_comprehension
```

```{r}
# Filter out 'self-rating' test parts
comprehension_data <- data_from_comprehension %>%
  filter(test_part != "self-rating")
comprehension_data
```

```{r}
# Calculate attempts to get each test part correct
attempts <- comprehension_data %>%
  group_by(subj_id, test_part) %>%
  mutate(attempt_number = cumsum(correct == FALSE & lag(correct, default = TRUE) == TRUE) + 1) %>%
  filter(correct) %>%
  summarize(attempts_to_correct = first(attempt_number), .groups = 'drop')
attempts
```


```{r}
summary_stats_comprehension <- attempts %>%
  group_by(test_part, attempts_to_correct) %>%
  summarise(num_people = n(), .groups = 'drop')
summary_stats_comprehension
```

```{r}
# Specify the order of test_part categories
test_part_order <- c("multichoice_nonpretend", "multichoice_leaderboard", "multichoice_tournament")
```


```{r plot_comprehension_checl_attempts, echo=FALSE, out.width ='75%'}
ggplot(summary_stats_comprehension, aes(x = factor(test_part, levels = test_part_order), y = num_people, fill = factor(attempts_to_correct))) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  labs(
    title = "Number of attempts to correct by comprehension check",
    x = "Test Part",
    y = "Number of People",
    fill = "Attempts to Correct"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels for better visibility
  )
```

It looks like the second comprehension check is causing some confusing, with more people than not taking 2 turns to answer it correclty. Perhaps this is somehting we can look to change. 


# Attention check

```{r}
data_from_attention
```


```{r}
#Need to remove the rows which have na 
data_from_attention_clean <- data_from_attention %>%
  filter(!is.na(last_word))
data_from_attention_clean
```


```{r}
#Make a dataframe with subj_id and the last word they was (5th word) - attention check always falls at the end. 
# Make a dataframe that is just subj_id and word

data_words <- pilot.df %>%
  filter(trial_type=='Hangman_replay') %>%
  dplyr::select(subj_id,word) 
data_words
```

```{r}
#Change reveal_word into a categorical variable
data_words$word <- factor(data_words$word)
data_words
```



```{r}
last_word_subj <- data_words %>%
  group_by(subj_id) %>%
  summarize(fifth_word = word[5])
last_word_subj
```


```{r}
#Now merge the two together
attention_check_full <- left_join(data_from_attention_clean, last_word_subj, by = "subj_id") 
attention_check_full
```


```{r}
#First convert fifth_word to character 
attention_check_full$fifth_word <- as.character(attention_check_full$fifth_word)
```



```{r}
#Now to check attention check pass rate: 
attention_check_full$letters_match <- tolower(attention_check_full$last_word) == tolower(attention_check_full$fifth_word)
attention_check_full
```


```{r}
attention_pass_counts <- table(attention_check_full$letters_match)
attention_pass_counts
```

 









































