---
title: "Quantifying the effects of privileged knowledge  on the
  perception of competence - Confirmatory Results"

author: 
  - name: "Nicole George"
    affiliation: "1"
  - name: "Matan Mazor"
    affiliation: "1"

affiliation:
  - id: "1"
    institution: "University of Oxford"

floatsintext: no
linenumbers: yes
draft: no
mask: no

figurelist: no
tablelist: no
footnotelist: no

classoption: "man"
output: papaja::apa6_word
---

```{r setup, include = FALSE}
library('groundhog')
groundhog.library(
  c(
    'papaja', #for apa formatting
    'pwr', # for power calculation
    'tidyverse', # for pipe %>%
    'emmeans',
    'afex',
    'dplyr'
  ), "2024-04-09"
)

knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, results='hide')
```


# Confirmatory Data Analysis 

## Rejection Criteria 

Participants that fail the attention check will be excluded.

```{r}
#Creating the filtered dataframe for analysis 
pilot.df <- read.csv("combined_pilot_batches.csv", na=c("")) %>%
  filter(!(word %in% c('', 'ZEBRA'))) %>%
  mutate(subj_id=PROLIFIC_PID)
pilot.df

#Create attention dataframe
data_from_attention <- pilot.df %>%
  filter(trial_type== 'survey-text') %>%
  dplyr::select(subj_id, last_word)
data_from_attention

#Need to remove the rows which have na 
data_from_attention_clean <- data_from_attention %>%
  filter(!is.na(last_word))
data_from_attention_clean

 
# Make a dataframe that is just subj_id and word
data_words <- pilot.df %>%
  filter(trial_type=='Hangman_replay') %>%
  dplyr::select(subj_id,word) 

#Change reveal_word into a categorical variable
data_words$word <- factor(data_words$word)
data_words

#Make a dataframe with subj_id and the last word they was (5th word); attention check always comes after the final word.
last_word_subj <- data_words %>%
  group_by(subj_id) %>%
  summarize(fifth_word = word[5])
last_word_subj

#Now merge the two together
attention_check_full <- left_join(data_from_attention_clean, last_word_subj, by = "subj_id") 
attention_check_full

#First convert fifth_word to character 
attention_check_full$fifth_word <- as.character(attention_check_full$fifth_word)

#Now to check attention check pass rate: 
attention_check_full$letters_match <- tolower(attention_check_full$last_word) == tolower(attention_check_full$fifth_word)
attention_check_full

#Now to filter to only include subjects which passed the attentionn check 
attention_check_pass <- attention_check_full %>%
  filter(letters_match == TRUE)
attention_check_pass
```

```{r} 
# Count the number of False for letters_match. This is the number of players which failed the attention check. 
false_count <- sum(!attention_check_pass$letters_match)
false_count
```
`r false_count` participants failed the attention, therefore none were excluded from the analysis. 


## Hypotheses

The purpose of this study is to examine the effect of access to privileged knowledge on participants’ perception of others’ competence in an online gamified experiment. 

Hypotheses will be tested using a series of 4 two-tailed repeated measures t-tests, with a significance level of 0.05. 
  

```{r}
data_from_games <- pilot.df %>%
  filter(trial_type=='Hangman_replay') %>%
  dplyr::select(subj_id,word,num_clicks) 
data_from_games

data_from_confidence <- read.csv("combined_pilot_batches.csv") %>%
  mutate(subj_id=PROLIFIC_PID,
         confidence=as.numeric(confidence_slider_self_response)) %>%
  group_by(subj_id) %>%
  summarise(
    confidence=mean(confidence,na.rm=T)
  )
data_from_confidence

data_from_guesses <- pilot.df %>%
  filter(trial_type=='Guess_leaderboard') %>%
  dplyr::select(subj_id,subject_pair,word,position,position_RT,true_position,reveal_word,player,distance, self_rating)
data_from_guesses
          
#Merge above to new usable, filtered dataframe
filtered_df <- data_from_games %>%
  merge(data_from_guesses) %>%
  merge(data_from_confidence)
filtered_df

#Change variables from characters to correct classification 
#Change reveal_word into a categorical variable
filtered_df$reveal_word <- factor(filtered_df$reveal_word)
#Change position into an integer variable 
filtered_df$position <- as.integer(filtered_df$position)
#Change true_position into an integer variable
filtered_df$true_position <- as.integer(filtered_df$true_position)
#Change distance into an integer variable 
filtered_df$distance <- as.integer(filtered_df$distance)
#Change self-rating into an integer
filtered_df$self_rating <- as.integer(filtered_df$self_rating)
#Change word into a categorical variable 
filtered_df$word <- factor(filtered_df$word)
#Change distance into an integer variable 
filtered_df$distance <- as.integer(filtered_df$distance)
#change confidence into an integer variable
filtered_df$confidence <- as.integer(filtered_df$confidence)

#Check variables were changed correctly
#Check class reveal_word
class(filtered_df$reveal_word)
#Check class position 
class(filtered_df$position)
#Check class true position 
class(filtered_df$true_position)
#check class distance 
class(filtered_df$distance)
#check class self rating
class(filtered_df$self_rating)
#check class word 
class(filtered_df$word)
#check class distance 
class(filtered_df$distance)
#check class confidence
class(filtered_df$confidence)

#Rename levels of reveal_word from true and false to revealed and hidden, respectively 
filtered_df$reveal_word <- factor(filtered_df$reveal_word, levels = c("true", "false"), labels = c("revealed", "hidden"))

# Check the levels of reveal_word variable
levels(filtered_df$reveal_word)

#Check changes in filtered_df (which we will be using for our analysis)
print(filtered_df)
```

```{r create-paired-df}
#Create Paired dataset for analysis
hidden_df <- filtered_df %>%
  filter(reveal_word=='hidden') 

revealed_df <- filtered_df %>%
  filter(reveal_word=='revealed') 

paired_df <- hidden_df %>%
  merge(revealed_df, by=c('subject_pair','word','player','true_position','num_clicks'),
        suffixes=c('.hidden','.revealed'))
paired_df
```

```{r mean-df-paired}
#Createdmean paired dataframe for position and self-rating analysis 
mean_df <- paired_df %>%
  group_by(subject_pair)%>%
  summarise(self_rating.hidden=mean(self_rating.hidden),
            self_rating.revealed=mean(self_rating.revealed),
            position.hidden=mean(position.hidden),
            position.revealed=mean(position.revealed),
            confidence.hidden=mean(confidence.hidden),
            confidence.revealed=mean(confidence.revealed),
            distance.hidden=mean(distance.hidden),
            distance.revealed=mean(distance.revealed))%>%
  mutate(self_rating.diff=self_rating.hidden-self_rating.revealed,
         position.diff=position.hidden-position.revealed,
         confidence.diff=confidence.hidden-confidence.revealed,
         distance.diff=distance.hidden-distance.revealed)
mean_df
```

### **Hypothesis 1 (position ranking):** 

We will test the null hypothesis that there is no difference in participants’ position ranking (on the leaderboard of the upcoming tournament of players) between the hidden outcome and revealed outcome conditions. A repeated measures t-test will be carried out on the paired participants between the hidden outcome and revealed outcome conditions. 

```{r}
meanPositionRev <- mean_df$position.revealed%>%mean()
meanPositionHid <- mean_df$position.hidden%>%mean()
sdPositionRev <- mean_df$position.revealed %>% sd()
sdPositionHid <- mean_df$position.hidden %>% sd()
t_test_result_position_pair <- t.test(mean_df$position.hidden, mean_df$position.revealed, paired = TRUE)
t_test_result_position_pair
```
#### *H1: no effect of outcome knowledge on predicted position*

A paired t-test was conducted to compare the mean scores of the revealed and the hidden outcome position ranking, on a scale of 1 (best) to 100 (worst). There was no significant difference in the scores for the revealed outcome (*M* =`r round(meanPositionRev, 2)`, *SD* =`r round(sdPositionRev, 2)`), and the hidden outcome condition (*M* =`r round(meanPositionHid, 2)`, *SD* =`r round(sdPositionHid, 2)`), and non-significant t-test result of 
(`r apa_print(t_test_result_position_pair)$full_result`).


### **Hypothesis 2 (accuracy):** 

We will test the null hypothesis that there is no difference in participants’ accuracy (the measure between participants position ranking of the player and the real ranking of the player) between the hidden outcome and revealed outcome conditions. A repeated measures t-test will be carried out on the paired participants between the hidden outcome and revealed outcome conditions. 

```{r}
meanDisRev <- mean_df$distance.revealed%>%mean()
meanDisHid <- mean_df$distance.hidden%>%mean()
sdDisRev <- mean_df$distance.revealed %>% sd()
sdDisHid <- mean_df$distance.hidden %>% sd()
t_test_result_accuracy_pair <- t.test(mean_df$distance.hidden, mean_df$distance.revealed, paired = TRUE)
t_test_result_accuracy_pair
```

#### *H2: no effect of outcome knowledge on prediction accuracy*

A paired sample repeated measures t-test was conducted to compare the accuracy (of the participants’ predicted position ranking of the player against the actual position ranking that player achieved in the supporting study) in the revealed and hidden outcome conditions. There was no significant difference in the absolute difference between the true and estimated scores in the revealed condition (*M* =`r round(meanDisRev, 2)`, *SD* =`r round(sdDisRev, 2)`) and the hidden condition (*M* = `r round(meanDisHid, 2)`, *SD* =`r round(sdDisHid, 2)`), and non-significant t-test result of 
(`r apa_print(t_test_result_accuracy_pair)$full_result`).


### **Hypotheses 3 (self-rating):**

We will test the null hypothesis that there is no difference in participants’ self-rating (participants ranking of themselves from 1st to 6th, had they played against the 5 players they watched) between the hidden outcome and revealed outcome conditions. A repeated measures t-test will be carried out on the paired participants between the hidden outcome and revealed outcome conditions. 

```{r}
meanSelfRev <- mean_df$self_rating.revealed%>%mean()
meanSelfHid <- mean_df$self_rating.hidden%>%mean()
sdSelfRev <- mean_df$self_rating.revealed %>% sd()
sdSelfHid <- mean_df$self_rating.hidden %>% sd()
t_test_result_self_rating_pair <- t.test(mean_df$self_rating.hidden, mean_df$self_rating.revealed, paired = TRUE)
t_test_result_self_rating_pair
```


#### *H3: no effect of outcome knowledge on self-rating*

A paired sample repeated measures t-test was conducted to compare the self-rating scores of the revealed and hidden outcome condition. Self-rating measured where the participants think they would have come out of 6 had they played against the 5 players they watched, from 1 (best) to 6 (worst). There was no significant difference in the scores for the the revealed condition (*M* = `r round(meanSelfRev, 2)`, *SD* = `r round(sdSelfRev, 2)`) and the hidden condition (*M* = `r round(meanSelfHid, 2)`, *SD* =`r round(sdSelfHid, 2)`), and non-significant t-test result of (`r apa_print(t_test_result_self_rating_pair)$full_result`).



### **Hypothesis 4 (confidence):** 

We will test the null hypothesis that there is no difference in participants’ confidence (of their self-rating) between the hidden outcome and revealed outcome conditions. A repeated measures t-test will be carried out on the paired participants between the hidden outcome and revealed outcome conditions. 

```{r}
meanConfRev <- mean_df$confidence.revealed%>%mean()
meanConfHid <- mean_df$confidence.hidden%>%mean()
sdConfRev <- mean_df$confidence.revealed %>% sd()
sdConfHid <- mean_df$confidence.hidden %>% sd()
t_test_result_confidence_pair <- t.test(mean_df$confidence.hidden, mean_df$confidence.revealed, paired = TRUE)
t_test_result_confidence_pair
```

#### *H4: no effect of outcome knowledge on confidence*

A paired sample repeated measures t-test was conducted to compare the mean confidence in self-rating score in the revealed and hidden outcome conditions. There was no significant difference in the scores for the revealed condition (*M* =`r round(meanConfRev, 2)`, *SD* =`r round(sdConfRev, 2)`) and the hidden condition (*M* = `r round(meanConfHid, 2)`, *SD* =`r round(sdConfHid, 2)`), and non-significant t-test result of (`r apa_print(t_test_result_confidence_pair)$full_result`).
. 









