---
title: "Quantifying the effects of privileged knowledge  on the
  perception of competence"
---

```{r setup, include = FALSE}
library('groundhog')
groundhog.library(
  c(
    'papaja', #for apa formatting
    'pwr', # for power calculation
    'tidyverse', # for pipe %>%
    'emmeans',
    'afex',
    'patchwork',
    'officer',
    'cowplot',
    'ggrepel',
    'dplyr'
  ), "2024-04-09"
)

knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, results='hide')
```


# Data Analysis 

## Rejection Criteria 

Participants that fail the attention check will be excluded.

```{r}
#Creating the filtered dataframe for analysis 
pilot.df <- read.csv("combined_pilot_batches.csv", na=c("")) %>%
  filter(!(word %in% c('', 'ZEBRA'))) %>%
  mutate(subj_id=PROLIFIC_PID)
pilot.df

#Create attention dataframe
data_from_attention <- pilot.df %>%
  filter(trial_type== 'survey-text') %>%
  dplyr::select(subj_id, last_word)
data_from_attention

#Need to remove the rows which have na 
data_from_attention_clean <- data_from_attention %>%
  filter(!is.na(last_word))
data_from_attention_clean

 
# Make a dataframe that is just subj_id and word
data_words <- pilot.df %>%
  filter(trial_type=='Hangman_replay') %>%
  dplyr::select(subj_id,word) 

#Change reveal_word into a categorical variable
data_words$word <- factor(data_words$word)
data_words

#Make a dataframe with subj_id and the last word they was (5th word); attention check always comes after the final word.
last_word_subj <- data_words %>%
  group_by(subj_id) %>%
  summarize(fifth_word = word[5])
last_word_subj

#Now merge the two together
attention_check_full <- left_join(data_from_attention_clean, last_word_subj, by = "subj_id") 
attention_check_full

#First convert fifth_word to character 
attention_check_full$fifth_word <- as.character(attention_check_full$fifth_word)

#Now to check attention check pass rate: 
attention_check_full$letters_match <- tolower(attention_check_full$last_word) == tolower(attention_check_full$fifth_word)
attention_check_full

#Now to filter to only include subjects which passed the attentionn check 
attention_check_pass <- attention_check_full %>%
  filter(letters_match == TRUE)
attention_check_pass
```


# Hypotheses

The purpose of this study is to examine the effect of access to privileged knowledge on participants’ perception of others’ competence in an online gamified experiment. 

  Hypotheses will be tested using a series of 4 two-tailed repeated measures t-tests, with a significance level of 0.05. 
  

```{r}
data_from_games <- pilot.df %>%
  filter(trial_type=='Hangman_replay') %>%
  dplyr::select(subj_id,word,num_clicks) 
data_from_games

data_from_confidence <- read.csv("combined_pilot_batches.csv") %>%
  mutate(subj_id=PROLIFIC_PID,
         confidence=as.numeric(confidence_slider_self_response)) %>%
  group_by(subj_id) %>%
  summarise(
    confidence=mean(confidence,na.rm=T)
  )
data_from_confidence

data_from_guesses <- pilot.df %>%
  filter(trial_type=='Guess_leaderboard') %>%
  dplyr::select(subj_id,subject_pair,word,position,position_RT,true_position,reveal_word,player,distance, self_rating)
data_from_guesses
          
#Merge above to new usable, filtered dataframe
filtered_df <- data_from_games %>%
  merge(data_from_guesses) %>%
  merge(data_from_confidence)
filtered_df

#Change variables from characters to correct classification 
#Change reveal_word into a categorical variable
filtered_df$reveal_word <- factor(filtered_df$reveal_word)
#Change position into an integer variable 
filtered_df$position <- as.integer(filtered_df$position)
#Change true_position into an integer variable
filtered_df$true_position <- as.integer(filtered_df$true_position)
#Change distance into an integer variable 
filtered_df$distance <- as.integer(filtered_df$distance)
#Change self-rating into an integer
filtered_df$self_rating <- as.integer(filtered_df$self_rating)
#Change word into a categorical variable 
filtered_df$word <- factor(filtered_df$word)
#Change distance into an integer variable 
filtered_df$distance <- as.integer(filtered_df$distance)
#change confidence into an integer variable
filtered_df$confidence <- as.integer(filtered_df$confidence)

#Check variables were changed correctly
#Check class reveal_word
class(filtered_df$reveal_word)
#Check class position 
class(filtered_df$position)
#Check class true position 
class(filtered_df$true_position)
#check class distance 
class(filtered_df$distance)
#check class self rating
class(filtered_df$self_rating)
#check class word 
class(filtered_df$word)
#check class distance 
class(filtered_df$distance)
#check class confidence
class(filtered_df$confidence)

#Rename levels of reveal_word from true and false to revealed and hidden, respectively 
filtered_df$reveal_word <- factor(filtered_df$reveal_word, levels = c("true", "false"), labels = c("revealed", "hidden"))

# Check the levels of reveal_word variable
levels(filtered_df$reveal_word)

#Check changes in filtered_df (which we will be using for our analysis)
print(filtered_df)
```

```{r create-paired-df}
#Create Paired dataset for analysis
hidden_df <- filtered_df %>%
  filter(reveal_word=='hidden') 

revealed_df <- filtered_df %>%
  filter(reveal_word=='revealed') 

paired_df <- hidden_df %>%
  merge(revealed_df, by=c('subject_pair','word','player','true_position','num_clicks'),
        suffixes=c('.hidden','.revealed'))
paired_df
```

```{r mean-df-paired}
#Createdmean paired dataframe for position and self-rating analysis 
mean_df <- paired_df %>%
  group_by(subject_pair)%>%
  summarise(self_rating.hidden=mean(self_rating.hidden),
            self_rating.revealed=mean(self_rating.revealed),
            position.hidden=mean(position.hidden),
            position.revealed=mean(position.revealed),
            confidence.hidden=mean(confidence.hidden),
            confidence.revealed=mean(confidence.revealed),
            distance.hidden=mean(distance.hidden),
            distance.revealed=mean(distance.revealed))%>%
  mutate(self_rating.diff=self_rating.hidden-self_rating.revealed,
         position.diff=position.hidden-position.revealed,
         confidence.diff=confidence.hidden-confidence.revealed,
         distance.diff=distance.hidden-distance.revealed)
mean_df
```

*Hypothesis 1 (position ranking):* We will test the null hypothesis that there is no difference in participants’ position ranking (on the leaderboard of the upcoming tournament of players) between the hidden outcome and revealed outcome conditions. A repeated measures t-test will be carried out on the paired participants between the hidden outcome and revealed outcome conditions. 

```{r}
mean_df$position.revealed%>%mean()
mean_df$position.hidden%>%mean()
mean_df$position.revealed%>%sd()
mean_df$position.hidden%>%sd()
t_test_result_position_pair <- t.test(mean_df$position.hidden, mean_df$position.revealed, paired = TRUE)
t_test_result_position_pair
```
```{r}
# Reshape the data to long format
mean_df_position_long <- gather(mean_df, key = "Condition", value = "Self_Rating", position.hidden, position.revealed)
mean_df_position_long
```

```{r}
mean_df_position_long$Condition <- as.factor(mean_df_position_long$Condition)
```

```{r}
mean_df_position_long <- mean_df_position_long %>%
  mutate(Condition = factor(Condition, levels = c("position.hidden", "position.revealed"))) %>%
  arrange(subject_pair, Condition) # Order by subject_pair and Condition
mean_df_position_long
```


```{r}
# Create the boxplot
p1 <- ggplot(mean_df_position_long, aes(x = Condition, y = Self_Rating)) +
  geom_boxplot(aes(fill = Condition), alpha = 0.2) + # Main boxplots with Condition as fill
  geom_jitter(aes(color = Condition), width = 0.2, size = 2) + # Individual data points
  labs(title = "Position by Condition",
       x = "Condition",
       y = "Position") +
  theme(text = element_text(size = 11, face = "bold"),
        plot.title = element_text(size = 12, face = "bold"),
         legend.position = "none")+
  scale_fill_manual(values = c('#99CC00', '#993399')) + # Colors for boxplots
  scale_color_manual(values = c('#99CC00', '#993399')) # Colors for jittered points

p1
```


*Hypotheses 2 (self-rating):* We will test the null hypothesis that there is no difference in participants’ self-rating (participants ranking of themselves from 1st to 6th, had they played against the 5 players they watched) between the hidden outcome and revealed outcome conditions. A repeated measures t-test will be carried out on the paired participants between the hidden outcome and revealed outcome conditions. 

```{r}
mean_df$self_rating.revealed%>%mean()
mean_df$self_rating.hidden%>%mean()
mean_df$self_rating.revealed%>%sd()
mean_df$self_rating.hidden%>%sd()
t_test_result_self_rating_pair <- t.test(mean_df$self_rating.hidden, mean_df$self_rating.revealed, paired = TRUE)
t_test_result_self_rating_pair
```

```{r}
# Reshape the data to long format
mean_df_selfrating_long <- gather(mean_df, key = "Condition", value = "Self_Rating", self_rating.hidden, self_rating.revealed)
```

```{r}
# Create the boxplot
p2 <- ggplot(mean_df_selfrating_long, aes(x = Condition, y = Self_Rating)) +
  geom_boxplot(aes(fill = Condition), alpha = 0.2) +
  geom_jitter(aes(color = Condition), width = 0.2, size = 2) +
  labs(title = "Self-Ratings by Condition",
       x = "Condition",
       y = "Self-Rating") +
  theme(text = element_text(size=11, face="bold"),
    plot.title = element_text(size=12, face="bold"),
     legend.position = "none")+
  scale_fill_manual(values = c('#99CC00', '#993399')) + # Colors for boxplots
  scale_color_manual(values = c('#99CC00', '#993399')) # Colors for jittered points

p2
```

*Hypothesis 3 (confidence):* We will test the null hypothesis that there is no difference in participants’ confidence (of their self-rating) between the hidden outcome and revealed outcome conditions. A repeated measures t-test will be carried out on the paired participants between the hidden outcome and revealed outcome conditions. 

```{r}
mean_df$confidence.revealed%>%mean()
mean_df$confidence.hidden%>%mean()
mean_df$confidence.revealed%>%sd()
mean_df$confidence.hidden%>%sd()
t_test_result_confidence_pair <- t.test(mean_df$confidence.hidden, mean_df$confidence.revealed, paired = TRUE)
t_test_result_confidence_pair
```
```{r}
# Reshape the data to long format
mean_df_confidence_long <- gather(mean_df, key = "Condition", value = "Self_Rating", confidence.hidden, confidence.revealed)
```

```{r}
# Create the boxplot
p3 <- ggplot(mean_df_confidence_long, aes(x = Condition, y = Self_Rating)) +
  geom_boxplot(aes(fill = Condition), alpha = 0.2) +
  geom_jitter(aes(color = Condition), width = 0.2, size = 2) +
  labs(title = "Confidence by Condition",
       x = "Condition",
       y = "Confidence") +
    theme(text = element_text(size=11, face="bold"),
    plot.title = element_text(size=12, face="bold"),
     legend.position = "none")+
  scale_fill_manual(values = c('#99CC00', '#993399')) + # Colors for boxplots
  scale_color_manual(values = c('#99CC00', '#993399')) 
p3
```

*Hypothesis 4 (accuracy):* We will test the null hypothesis that there is no difference in participants’ accuracy (the measure between participants position ranking of the player and the real ranking of the player) between the hidden outcome and revealed outcome conditions. A repeated measures t-test will be carried out on the paired participants between the hidden outcome and revealed outcome conditions. 

```{r}
mean_df$distance.revealed%>%mean()
mean_df$distance.hidden%>%mean()
mean_df$distance.revealed%>%sd()
mean_df$distance.hidden%>%sd()
t_test_result_accuracy_pair <- t.test(mean_df$distance.hidden, mean_df$distance.revealed, paired = TRUE)
t_test_result_accuracy_pair
```
```{r}
# Reshape the data to long format
mean_df_accuracy_long <- gather(mean_df, key = "Condition", value = "Self_Rating", distance.hidden, distance.revealed)
```

```{r}
# Create the boxplot
p4 <- ggplot(mean_df_accuracy_long, aes(x = Condition, y = Self_Rating)) +
  geom_boxplot(aes(fill = Condition), alpha = 0.2) +
  geom_jitter(aes(color = Condition), width = 0.2, size = 2) +
  labs(title = "Accuracy by Condition",
       x = "Condition",
       y = "Accuracy") +
  theme(text = element_text(size=11, face="bold"),
    plot.title = element_text(size=12, face="bold"),
    legend.position = "none")+
  scale_fill_manual(values = c('#99CC00', '#993399')) + # Colors for boxplots
  scale_color_manual(values = c('#99CC00', '#993399')) 
p4
```


```{r}
# Combine plots using cowplot
combined_plot1 <- plot_grid(p1, p4, ncol = 2)
combined_plot1
ggsave(file="confirmatory plots/combinedBoxplot1.png")
```



```{r}
# Combine plots using cowplot
combined_plot2 <- plot_grid(p2, p3, ncol = 2)
combined_plot2
ggsave(file="confirmatory plots/combinedBoxplot2.png")
```






