---
title: "R Notebook"
output: html_notebook
---

Code based on : 

https://github.com/matanmazor/ignorance/blob/main/docs/hangman.Rmd

```{r}
library(groundhog)

groundhog.library(c(
  'png',
  'grid',
  'ggplot2',
  'svglite',
  'xtable',
  'papaja',
  'tidyverse',
  'broom',
  'cowplot',
  'reticulate',
  'MESS', # for AUCs
  'lsr', # for effect sizes
  'pwr', # for power calculations
  'brms', # for mixed effects modeling
  'BayesFactor', # for Bayesian t test
  'jsonlite', # parsing data from sort_trial
  'caret', #for cross validation
  'ggrepel', #for ggplot words
  'caret', #for cross validation
  'kernlab' #for SVM
), '2024-04-09')
```


Load csv 

```{r}
speed.df <- read.csv('combined_data_speed.csv',na.strings=c(""," ","NA")) %>%
  rename(subj_id = PROLIFIC_PID) %>%
   filter(!(word %in% c('', 'ZEBRA'))) %>%
  mutate(subj_id = factor(subj_id))
speed.df
```

Format Data 

```{r}
position_df <- speed.df %>%
  filter(trial_type== 'Guess_leaderboard') %>%
  dplyr::select(subj_id, subject_pair, word, position)
position_df
```


```{r}

speed.click_df <- speed.df %>%
 filter(trial_type=='Hangman_replay') %>%
  dplyr::select(subj_id, subject_pair,
         reveal_word, 
         word,
         num_clicks,
         click_log) 
speed.click_df
```

Make a dataframe for later use with all of the relevant information merged from the two dataframes above

```{r}
speed.relevant.df <- speed.click_df %>%
  merge(position_df) 
speed.relevant.df
```


```{r}
speed.click_df <- speed.click_df %>%
  rowwise()%>%
  mutate(num_hits = strsplit(gsub(' ','',word),split='')[[1]]%>%unique()%>%length(),
         click_log = gsub("\'","\"", click_log),
         click_log = gsub("None","null", click_log),
         word = factor(word,levels=c(
           'KENTUCKY',
           'HAWAII',
           'USAIN BOLT',
           'SHAKIRA',
           'FIG',
           'NECTARINE',
           'WRIST',
           'THUMB',
           'THIRTY FOUR'
         ))) 
speed.click_df
```


```{r}

speed.click_log <- data.frame(matrix(ncol=9,nrow=0, 
                               dimnames=list(NULL, 
                                             c("subj_id",
                                              "test_part", 
                                              "word",
                                              "num_clicks",
                                              "letter",
                                              "hit",
                                              "t",
                                              "reveal_word",
                                              "click_number"))))


for (row in 1:nrow(speed.click_df)) {
  
    subject_click_log <- data.frame(fromJSON(speed.click_df[row, ]$click_log)) %>%
    mutate(
      letter = lead(letter,1),
      t = lead(t,1),
      hit = lead(hit,1),
      click_number = 1:n(),
      subj_id = speed.click_df[row, ]$subj_id,
      word = speed.click_df[row, ]$word,
      reveal_word = speed.click_df[row, ]$reveal_word,
      num_clicks = speed.click_df[row, ]$num_clicks
    )%>%
      filter(click_number<=num_clicks)
    
    speed.click_log <- rbind(speed.click_log, subject_click_log);
}
    

speed.click_log <- speed.click_log %>%
  relocate(subj_id, .before = letter) %>%
  relocate(word, .before=letter) %>% 
  relocate(reveal_word, .before=letter) %>% 
  relocate(click_number, .before=letter) %>%
  group_by(subj_id,word) %>%
  mutate(RT=t-lag(t,default=0)) %>%
  group_by(subj_id,word) %>%
  rowwise()

speed.click_log
```


```{r}
speed.total_time_df <- speed.click_log %>%
 filter(click_number==num_clicks)%>%
  mutate(t=t/1000)
speed.total_time_df
```

```{r}
speed.time.word.subj.df <- speed.total_time_df %>%
  select(subj_id, word, t)
speed.time.word.subj.df
```

```{r}
write.csv(speed.time.word.subj.df, file = "speed.time.word.csv")
```

```{r}
plotSpeed <- speed.total_time_df %>%
  ggplot(aes(x=word,y=t)) +
  geom_boxplot() +
  scale_y_continuous(limits=c(0,100))
plotSpeed
```

Correlation 

```{r}
speed_complete.df <- speed.total_time_df %>%
  merge(speed.relevant.df)
speed_complete.df
```

```{r}
mean_speed_df <- speed_complete.df %>%
  group_by(word) %>%
 summarize(mean_speed = mean(t))
mean_speed_df
```
 
```{r}
mean_position_df <- speed_complete.df %>%
  group_by(word) %>%
  summarize(mean_position = mean(position)) 
mean_position_df
```
Merge 

```{r}
mean_speed_position_df <- mean_position_df %>%
  merge(mean_speed_df) 
mean_speed_position_df
```


Correlation between word speed and position 

```{r}
correlation_speed_pos <- cor.test(mean_speed_position_df$mean_position, mean_speed_position_df$mean_speed)
correlation_speed_pos
```

A Pearson's product-moment correlation was conducted to examine the relationship between mean position and mean speed. The analysis revealed a positive correlation between these variables, though the relationship was not statistically significant, r(7)=0.53, p=.14. The 95% confidence interval for the correlation ranged from −0.20 to 0.88, suggesting uncertainty about the true strength of the relationship.




```{r}
speed_split.df <- speed.total_time_df %>%
  merge(speed.df) %>%
   spread(reveal_word,t)
speed_split.df
```

```{r}
speed_split.df <- speed_split.df %>%
  rename(
    hidden = `False`,
    revealed = `True`
  )
speed_split.df
```

```{r}
speed_split_pair.df <- speed_split.df %>%
  arrange(subject_pair) %>%  # Arrange data by subject_pair
  select(-subj_id) 
speed_split_pair.df
```




BY SUBJ_ID

t is time. Want to look at the correlation between speed of game and predicted score given 
So will end up with 200 values, each one is a correlation per subject (correlation of ther 5 games)

```{r}
speed_complete.df
```


```{r}
#Define a function to calculate correlation for each participant
calc_correlation <- function(data) {
  cor(data$t, data$position, use = "complete.obs")
}
```


```{r}
#Apply the function to each participant
correlation_speed <- speed_complete.df %>%
  group_by(subj_id) %>%
  summarise(correlation = calc_correlation(cur_data()))
correlation_speed
```

```{r}
# Perform a one-sample t-test to see if the mean correlation is different from 0
t_test_pop <- t.test(correlation_speed$correlation, mu = 0)
t_test_pop
```

A one-sample t-test revealed a significant positive mean correlation between speed and the measured variable, t(197)=10.32,p<.001. The 95% confidence interval for the mean correlation ranged from 0.28 to 0.41, with a sample mean of M=0.34. This suggests a robust positive relationship.


Make a dataframe for revealed and for hidden 

```{r}
revealed_speed.df <- speed_complete.df %>% filter(reveal_word == "True")
hidden_speed.df <- speed_complete.df %>% filter(reveal_word == "False")
```

```{r}
revealed_speed.df
hidden_speed.df
```


```{r}
#Apply the function to each participant
correlation_speed_revealed <- revealed_speed.df %>%
  group_by(subj_id) %>%
  summarise(correlation_revealed = calc_correlation(cur_data()))
correlation_speed_revealed
```

```{r}
# Perform a one-sample t-test to see if the mean correlation is different from 0
t_test_revealed_speed <- t.test(correlation_speed_revealed$correlation_revealed, mu = 0)
t_test_revealed_speed
```

A one-sample t-test indicated a significant positive mean correlation between speed and the measured variable in the revealed condition, t(99)=5.74,p<.001. The 95% confidence interval for the mean correlation was [0.18, 0.38], with a sample mean of M=0.28. This suggests a moderate positive relationship.


```{r}
#Apply the function to each participant
correlation_speed_hidden <- hidden_speed.df %>%
  group_by(subj_id) %>%
  summarise(correlation_hidden = calc_correlation(cur_data()))
correlation_speed_hidden
```

```{r}
# Perform a one-sample t-test to see if the mean correlation is different from 0
t_test_hidden_speed <- t.test(correlation_speed_hidden$correlation_hidden, mu = 0)
t_test_hidden_speed
```

A one-sample t-test revealed a significant positive mean correlation between speed and the measured variable in the hidden condition, t(97)=9.19,p<.001. The 95% confidence interval for the mean correlation was [0.32, 0.49], with a sample mean of M=0.40. This indicates a strong positive relationship.

Combine datasets 

```{r}
t_test_result <- t.test(correlation_speed_hidden$correlation_hidden, correlation_speed_revealed$correlation_revealed, var.equal = TRUE)
t_test_result
```




















































